Missing The Point

### 2020-09-22 Manuscript.Rmd
Add example of diagnostics with boys data

# functions
source("~/MissingeThePoint/R/ComputeDiagnostics.R")

@@

impute_once <- function(iteration, ...) {
  if(is.null(mids)){
    mids <<- mice(boys, m = n_imp, maxit = 1, printFlag = FALSE)
  }
  else {
    mids <<- mice.mids(mids, printFlag = FALSE)
  }
  mira <- mids %>% mice::lm.mids(age ~ ., data = .) 
  mipo <- mira %>%
    mice::pool() %>%
    summary(., conf.int = TRUE)
  out <- data.frame(it = iteration, est = mipo[["estimate"]][2])
  return(out)
}

# parameters
n_imp <- 5
n_it <- 10

# analyses
mids <- NULL
ests <- purrr::map_dfr(1:n_it, function(it){impute_once(iteration = it)})
param <- preprocess_thetas(mids$chainMean, ext = "mu") %>% 
  dplyr::full_join(
      preprocess_thetas(mids$chainVar, ext = "sigma")
  )
convs <- get_diagnostics(param)
res <- full_join(ests, convs)
# plot
ggplot(conv, aes(x = it, y = ac.max.mu.hgt)) +
  geom_line()

# more analyses
imp2 <- mice(boys, m = n_imp, maxit = 1, printFlag = FALSE, seed = 123)
mice.mids(imp2)
```

>>>>

# functions
source("~/MissingThePoint/R/ComputeDiagnostics.R")

@@

impute_once <- function(iteration, ...) {
  if(is.null(mids)){
    mids <<- mice(boys, m = n_imp, maxit = 1, seed = 123, printFlag = FALSE)
  }
  else {
    mids <<- mice.mids(mids, printFlag = FALSE)
  }
  mira <- mids %>% mice::lm.mids(age ~ ., data = .) 
  mipo <- mira %>%
    mice::pool() %>%
    summary(., conf.int = TRUE)
  mild <- mids %>% mice::complete("all")

  qhat <- 
      map_dbl(mild, ~ {
        lm(formula = age ~ ., data = .) %>% .$coefficients %>% .[2]
      })
  lambda <- mild %>%
      purrr::map_dbl(., ~ {
        dplyr::mutate(., dplyr::across(dplyr::everything(), ~as.numeric(.))) %>% 
        princomp(., cor = TRUE) %>% .$sdev %>% .[1] %>% . ^ 2 #first eigenvalue of the varcovar matrix
      })
  qhats <<- rbind(qhats, data.frame(it = iteration, m = 1:n_imp, qhat = qhat))
  lambdas <<- rbind(lambdas, data.frame(it = iteration, m = 1:n_imp, lambda = lambda))

  out <- data.frame(it = iteration, est = mipo[["estimate"]][2])
  return(out)
}

# parameters
n_imp <- 5
n_it <- 20

# analyses
mids <- qhats <- lambdas <- NULL
ests <- purrr::map_dfr(1:n_it, function(it){impute_once(iteration = it)})
mids <- mice(boys, m = n_imp, maxit = n_it, seed = 123, printFlag = FALSE)
param <- preprocess_thetas(mids$chainMean, ext = "mu") %>% 
  dplyr::full_join(
      preprocess_thetas(mids$chainVar, ext = "sigma") %>% 
        dplyr::full_join(qhats) %>% 
        dplyr::full_join(lambdas)
  )
convs <- get_diagnostics(param)
res <- full_join(ests, convs)

# plot
ggplot(res, aes(x = it, y = est)) +
  geom_line()
ggplot(res, aes(x = it, y = ac.max.mu.hgt)) +
  geom_line()
ggplot(res, aes(x = it, y = ac.max.qhat)) +
  geom_line()
ggplot(res, aes(x = it, y = ac.max.lambda)) +
  geom_line()
ggplot(res, aes(x = it, y = r.hat.max.mu.hgt)) +
  geom_line()
ggplot(res, aes(x = it, y = r.hat.max.qhat)) +
  geom_line()
ggplot(res, aes(x = it, y = r.hat.max.lambda)) +
  geom_line()
